A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-22 manuscript/manuscript.tex
glossary

    \item $\mathbf{B}^*$: A $(m+1) \times p$ matrix constructed by row binding $\boldsymbol\psi^T$. to $\mathbf{B}$.

@@

>>>>

    \item $\mathbf{B}^*$: A $(m+1) \times p$ matrix constructed by row binding $\boldsymbol\psi^T$ to $\mathbf{B}$.

@@

The multivariate skew-normal regression model can be written as follows.

$$\mathbf{Y} = \mathbf{X}\mathbf{B} + \mathbf{t} \boldsymbol\psi^T + \mathbf{E} = \mathbf{X}^* \mathbf{B}^* + \mathbf{E}$$

Under the assumption that $t_i \stackrel{iid}{\sim}T_[0,\infty)(0,1)$ and that $\mathbf{E}$ is made of row vectors $\boldsymbol\epsilon_i = (\epsilon_{i1},...,\epsilon_{ip})$ for $i = 1,...,n$,
